\section{Tentative Project Budget}


One of the first rules of engineering is to make your product as cost efficient as possible. Everyone wants to save money, from the company designing the product, to the person buying the product, so sourcing reasonably-priced materials is high on the priority list. Our initial budget estimate fell somewhere between \$136.45 and \$181.45, as shown in Table \ref{tab:budget} below. As with most initial estimates, it is anticipated that number will change as we refine our design over the life of the project.\hfill

\begin{table}[H]
\spiceitup
\caption{Proposed Budget}
\begin{tabular}{c|c|c}
Quantity Needed & Item Description & Price (USD) \\ \hline
1 & Solar Panel & \$29.00 \\
1 & DC/Lithium-poly Charger & \$17.50 \\
1 & Lithium-poly Battery & \$14.95 \\
1 & Powerboost 500 & \$10.00 \\
1 & IMU & \$15.00 \\
1 & WiFi-Enabled Raspberry Pi & \$35.00 \\
Unknown & 3D-Printing Material & \$15.00 – \$60.00 per roll \\
 & \multicolumn{1}{r|}{\textbf{Total Estimated Cost}} & \multicolumn{1}{l}{\textbf{\$136.45 - \$181.45}}
\end{tabular}
\centering
\label{tab:budget}
\end{table}

This initial estimate is based off of a design with only one IMU; however we may need to add up to three more in order to achieve the desired sensitivity level. The 3D-printed shell is another price hurdle. It has yet to bet determined whether it would be more cost-efficient to print the shell ourselves or outsource that portion of the design. Factors to take into consideration include the types of 3D printers at our disposal and whether or not the printing material compatible with those machines would be an appropriate choice for our design. 

Most surface pool alarms, such as \juicy, are usually priced in the \$150 to \$200 range. \juicy will have to be marketed within that price range to be considered a competitive device, which means that production costs will need to be reduced in order to maximize profit. Efforts will be made throughout the duration of the project to find the most cost-efficient materials that meet certain quality standards that have been set forth by the team.