\section{3D Printing Materials}



The casing of the pool alarm must be water-tight in order to prevent damage to the sensitive electronic components inside, buoyant, and durable enough to withstand day after day of sun and water exposure. So far the best option appears to be 3D-printing the case, but with which material? With all of the advances in 3D-printing technology, there are multiple types of plastic filament that appear to be viable options. Others, such as poly lactic acid (PLA) and polyvinyl alcohol (PVA), were quickly ruled out due to their intolerance to water.

Acrylonitrile Butadiene Styrene (ABS), stereolithography (SLA; also known as resin printing), and PETG, a glycol-modified version of Polyethylene Terephthalate are all still viable options. Unfortunately, no material appears to stand out above the rest at this point in time. Each plastic has several pros and cons, as laid out in Table \ref{tab:material} below.\hfill

\begin{table}[H]
\caption{Comparison Printer Material}
\begin{tabular}{c|c|c|c|}
\cline{2-4}
 & ABS & SLA & PETG \\ \hline
Pros & \makecell{Very sturdy\\ Long lifespan\\ Easy to process} & \makecell{Very economic\\ High wear resistance} & \makecell{Recyclable\\ Rugged\\ Exceptional layer adhesion} \\ \hline
Cons & \makecell{Damages in direct sunlight\\ Not biodegradable} & \makecell{More expensive\\ Not suitable for outdoor use} & \makecell{Can be sticky\\ Less resistance to scratches} \\ \hline
\end{tabular}
\centering
\label{tab:material}
\end{table}

ABS is by far the most popular option. It is used in most modern manufactured products, including LEGOs, keyboard keys, and the plastic face-guard on wall sockets \cite{abs}. It is reported to be durable, relatively inexpensive, and easy to process. However, many sources caution that ABS is susceptible to damage from direct sun exposure. Tests have yet to be run to determine the extent of the damage, so for now, ABS is still in the running.

SLA appears to be the most water-tight option as its very small layer heights almost eliminate the layer lines common among 3D printers \cite{sla}. Although SLA is friendlier to the environment and more resistant to wear and tear, it is more expensive. Despite its many great qualities, SLA may be off the table for the simple fact that it stretches an already tight budget.

PETG is another excellent choice, especially for water proof applications. PETG is commonly used to manufacture water bottles, and is chemically resistant so exposure to pool chemicals should not be an issue. It is reported to have a long lifespan, and is also recyclable. Although PETG is easily scratched, that appears to be one of its only drawbacks, making it a fantastic choice for \juicy’s shell.